---
title: 'Figures 2, S1 for:'
subtitle: 'TBD'
author: 'Matthew J. Michalska-Smith & Stefano Allesina'
output: 
  html_document: 
    highlight: pygments
---

## Import libraries
```{r, message=FALSE}
library(knitr)
library(tidyr)
library(dplyr)
library(ggplot2)
library(stringr)
```

## Global parameters
```{r}
INTERVAL_START <- 1991
INTERVAL_END <- 2010
cols <- c("#6780d8", "#b84c3e")
```

## Read in the data for plotting
```{r}
load(paste0("../Figures/PairwiseComparison_", INTERVAL_START, "-", INTERVAL_END, ".RData"))
```

## Some aesthetic restructuring
```{r}
results <- results %>%
    mutate(rand = factor(ifelse(rand,
                                "Randomized",
                                "National Academy Scientists          ")),
           concordance = concordance-(1-concordance))
```

# Plotting
## Figure 1
```{r}
ggplot(results %>% filter(sum_stat != "All Pairs", nyears == 1)) +
    aes(y=concordance, x=rand, colour=rand, fill=rand) +
    geom_violin() +
    geom_hline(yintercept=0) +
    geom_boxplot(width=0.2, alpha=0.5, fill="white", colour="black", outlier.stroke=0.5) +
    scale_linetype_identity() +
    scale_colour_manual(values=cols) + scale_fill_manual(values=cols) +
    ylab("Correlation between Quality and Quantity") +
    facet_wrap(~sum_stat, nrow=1) +
    theme_bw() + theme(legend.position   = "bottom",
                       legend.title      = element_blank(),
                       legend.background = element_blank(),
                       axis.text.x       = element_blank(),
                       axis.title.x      = element_blank(),
                       axis.ticks.x      = element_blank())
ggsave(paste0("../Figures/Figure1_", INTERVAL_START, "-", INTERVAL_END, ".pdf"),
       width=9.75, height=5.25)
```
Violin plots of the strength of pairwise correlation between quantity and quality
for members of the National Academy of Sciences.  The panels are divided based on
which summary statistic is being compared across years. A value of 1 (-1) indicates
that, for every pair of adjacent years, the more productive one had a higher
(lower) statistic (\emph{e.g.} maximally cited paper published in that
year). A value of $0$ (horizontal black line) indicates that the larger statistic
is equally likely to be from the more or less productive year. In blue (left in
each plot) are the empirically observed correlation values for each author. In red
(right in each plot) are the correlation values observed when citation counts were
randomized within each author's corpus.

## Figure S1
```{r}
ggplot(results %>% filter(sum_stat != "All Pairs", nyears == 1)) +
    aes(y=concordance, x=rand, colour=rand, fill=rand) +
    geom_violin() +
    geom_hline(yintercept=0) +
    geom_boxplot(width=0.2, alpha=0.5, fill="white", colour="black", outlier.stroke=0.5) +
    geom_segment(aes(x=as.integer(xx)-0.1, xend=as.integer(xx)+0.1, yend=concordance),
                 data=results %>%
                     mutate(xx=as.factor(ifelse(rand == levels(rand)[1],
                                                levels(rand)[2],
                                                levels(rand)[1]))) %>%
                     group_by(nyears, sum_stat, rand, xx) %>%
                     summarise(concordance = median(concordance))) +
    scale_linetype_identity() +
    scale_colour_manual(values=cols) + scale_fill_manual(values=cols) +
    ylab("Correlation between Quality and Quantity") +
    facet_grid(nyears~sum_stat) +
    theme_bw() + theme(legend.position   = "bottom",
                       legend.title      = element_blank(),
                       legend.background = element_blank(),
                       axis.text.x       = element_blank(),
                       axis.title.x      = element_blank(),
                       axis.ticks.x      = element_blank())
ggsave(paste0("../Figures/PairwiseComparison_", INTERVAL_START, "-", INTERVAL_END, ".pdf"),
       width=15, height=10)
```
Add caption.
